{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Analysis, Convergence, and Applications }

### 2024-12-13 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

    \begin{lemma}[Proximal gradient envelope] 
        Fix any $y$, we will have for all $x \in \RR^n$ that: 
        \begin{align*}
            \widetilde{\mathcal M}^{L^{-1}}(x; y)
            &= 
            \mathcal M^{L^{-1}}(x; y)- D_f(x, y) \ge \mathcal M^{L^{-1}}(x; y). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        \begin{align*}
            \widetilde{\mathcal M}^{L^{-1}}(x; y) 
            &= 
            g(x) + f(y) + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
            \\
            &= 
            g(x) + f(x) - f(x) + f(y) 
            + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
            \\
            &= 
            F(x) - D_f(x, y) + \frac{L}{2}\Vert x - y\Vert^2 
            \\
            &= \mathcal M^{L^{-1}}(x; y) - D_f(x, y). 
        \end{align*}
    \end{proof}

@@

        Use $\mu = D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2$ also works, $\mu$ is a pessimistic choice for the inequality above. 

@@

        But in general the choice of $\mu$ remains the strong convexity modulus or equivalently, any value that is smallar than the true strong convexity constant for claiming the convergence rate for all initial guesses. 

@@

            The choice of $\rho_k$ allows for divergence to traditional choices of step sizes in the literatures. 

@@

    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        For all $k\ge 0$, iterates $(w_t, y_t, x_{t + 1}, z_{t + 1})$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_t + \tau_t = L\delta_t$. Then 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_t, \tau_t, \delta_t$ such that there exists $\theta_t$ satisfying: 
        \begin{align*}
            v_{t + 1} - x_{t + 1} 
            &= \theta_t(x_{t + 1} - x_t)
        \end{align*}
        To verify, do 
        \begin{align*}
            v_{t + 1} &= 
            (1 + \xi_t)^{-1}(v_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            & \textcolor{gray}{
                v_t = (1 + \tau_t)y_t - \tau_t x_t
            }
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t)y_t - \tau_t x_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t x_t - \delta_t \mathcal G_L(y_t))
            \\
            v_{t + 1} - x_{t + 1}
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t x_t - \delta_t \mathcal G_L(y_t))
            - (y_t - L^{-1}\mathcal G_Ly_t)
            \\
            &= 
            (1 + \xi_t)^{-1}(\tau_ty_t - \tau_t x_t - \delta_t \mathcal G_L(y_t))
            + L^{-1}\mathcal G_Ly_t
            \\
            &= 
            (1 + \xi_t)^{-1}
            \left(
                \tau_ty_t - \tau_t x_t + (L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
            \\
            &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(
                y_t - x_t + 
                \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
        \end{align*}
        The RHS is can be verified through 
        \begin{align*}
            x_{t + 1} - x_t &= 
            y_t - L^{-1}\mathcal G_L(y_t) - x_t
            \\
            &= (y_t - x_t) - L^{-1}\mathcal G_L(y_t). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) 
            &= - L^{-1}
            \\
            (1 + \xi_t) - L\delta_t
            &= 
            - \tau_t
            \\
            1 + \xi_t + \tau_t
            &=
            L\delta_t. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            v_{t + 1} - x_{t + 1} &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(y_t - x_t - L^{-1}\mathcal G_L(y_t)\right) 
            = 
            (1 + \xi_t)^{-1}\tau_t(x_{t + 1} - x_t). 
        \end{align*}
    \end{proof}

@@

    \end{definition}
    \begin{remark}
        \textcolor{red}
        {
        There exists a choice of $\rho_k \in [0, 1), \mu = 0$ such that the above algorithm is equivalent to Chambolle Dossal 2015 \cite{chambolle_convergence_2015}. 
        When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
        When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
        \begin{align*}
            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
        \end{align*}
        Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
        Substituting it back to the momentum form of R-WAPG, we recovers the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
        }
    \end{remark}

\subsection{Representing algorithms in the literatures via R-WAPG}
\subsection{The method of Spectral Momentum}
\subsection{Numerical experiments and applications}

>>>>

    \begin{lemma}[Proximal gradient envelope] 
        Fix any $y$, we will have for all $x \in \RR^n$ that: 
        \begin{align*}
            \widetilde{\mathcal M}^{L^{-1}}(x; y)
            &= 
            \mathcal M^{L^{-1}}(x; y)- D_f(x, y) \le \mathcal M^{L^{-1}}(x; y). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        \begin{align*}
            \widetilde{\mathcal M}^{L^{-1}}(x; y) 
            &= 
            g(x) + f(y) + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
            \\
            &= 
            g(x) + f(x) - f(x) + f(y) 
            + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
            \\
            &= 
            F(x) - D_f(x, y) + \frac{L}{2}\Vert x - y\Vert^2 
            \\
            &= \mathcal M^{L^{-1}}(x; y) - D_f(x, y). 
        \end{align*}
    \end{proof}

@@

        Use $\mu = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2$ also works on (4*), $\mu$ is a pessimistic choice for the inequality above. 

@@

        But in general the choice of $\mu$ remains the strong convexity modulus or equivalently, any value that is smaller than the true strong convexity constant for claiming the convergence rate for all initial guesses. 

@@

            The choice of $\rho_k$ allows for untraditional choices of step sizes in the literatures. 

@@

    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        For all $k\ge 0$, iterates $(w_t, y_t, x_{t + 1}, z_{t + 1})$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_k + \tau_k = L\delta_k$. Then 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_k, \tau_k, \delta_k$ such that there exists $\theta_k$ satisfying: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} 
            &= \theta_t(x_{k + 1} - x_k).
        \end{align*}
        To verify, do 
        \begin{align*}
            v_{k + 1} &= 
            (1 + \xi_k)^{-1}(v_k + \xi_t y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k)y_k - \tau_t x_k + \xi_k y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            \\
            v_{k + 1} - x_{k + 1}
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_t - \tau_k x_k - \delta_t \mathcal G_L(y_k))
            - (y_k - L^{-1}\mathcal G_Ly_k)
            \\
            &= 
            (1 + \xi_k)^{-1}(\tau_ky_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            + L^{-1}\mathcal G_Ly_k
            \\
            &= 
            (1 + \xi_k)^{-1}
            \left(
                \tau_ty_k - \tau_t x_k + (L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right)
            \\
            &= 
            (1 + \xi_k)^{-1}\tau_k
            \left(
                y_k - x_k + 
                \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right).
        \end{align*}
        Going between the first and second inequality we used $v_k = (1 + \tau_k)y_k - \tau_k x_k$ which is an rearranged $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$. 
        The RHS is can be verified through 
        \begin{align*}
            x_{k + 1} - x_k &= 
            y_t - L^{-1}\mathcal G_L(y_k) - x_k
            \\
            &= (y_k - x_k) - L^{-1}\mathcal G_L(y_k). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_t^{-1}(L^{-1}(1 + \xi_k) - \delta_k) 
            &= - L^{-1}
            \\
            (1 + \xi_k) - L\delta_k
            &= 
            - \tau_k
            \\
            1 + \xi_k + \tau_k
            &=
            L\delta_k. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} &= 
            (1 + \xi_k)^{-1}\tau_t
            \left(y_k - x_k - L^{-1}\mathcal G_L(y_k)\right) 
            = 
            (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
        \end{align*}
    \end{proof}

@@

    \end{definition}
    \begin{remark}
        \textcolor{red}
        {
        There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle Dossal 2015 \cite{chambolle_convergence_2015}. 
        When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
        When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
        \begin{align*}
            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
        \end{align*}
        Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
        Substituting it back to the momentum form of R-WAPG, we recovers the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
        }
    \end{remark}

\subsection{Representing algorithms in the literatures via R-WAPG}

\subsection{The method of Spectral Momentum}

\subsection{Numerical experiments and applications}

### 2024-12-13 Notebook LaTEX/Proposal/main.tex
>w<, changes

    \par
    Our ongoing research concerns accelerated proximal gradient type method for solving (\ref{eqn:additive-comp-obj}). 
    In the expository writing by Walkington \cite{noel_nesterovs_nodate}, a variant for of accelerated gradient method for strongly convex function $f$ is discussed. 
    We had two lingering questions after reading it. 
    \begin{enumerate}
        \item Do there exist a unified description for the convergence for both variants of the algorithm. 
        \item Is it possible to attain faster convergence rate without knowledge about the strong convexity of function $f$. 
    \end{enumerate}
    The good news is we have definitive answers for both questions through our own efforts of research. 
    Section \ref{sec:unify-nes-acceleration}, \ref{sec:spectral-momentum} are our ongoing research which present the answers to the questions. 
    \par
    In Section \ref{sec:unify-nes-acceleration}, we proposed the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures. 
    The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures. 
    The descriptive power of R-WAPG allows convergence analysis for all the variants using one single theorem. 
    \par
    In Section \ref{sec:spectral-momentum} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior. 
    Results of numerical experiments are presented. 
    \par
    Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
    It's based on a series of papers (CITATION HERE) in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
    We will point out potential future direction of research of Catalyst acceleration. 
    \par

@@

\section{Using PostGreSQL and big data analytic method for species classification on Sentinel-2 Satelite remote sensing imagery}

>>>>

    \par
    Our ongoing research concerns accelerated proximal gradient type method for solving (\ref{eqn:additive-comp-obj}). 
    In the expository writing by Walkington \cite{noel_nesterovs_nodate}, a variant for of accelerated gradient method for strongly convex function $f$ is discussed. 
    We had two lingering questions after reading it. 
    \begin{enumerate}
        \item Do there exist a unified description for the convergence for both variants of the algorithm. 
        \item Is it possible to attain faster convergence rate without knowledge about the strong convexity of function $f$. 
    \end{enumerate}
    The good news is we have definitive answers for both questions through our own efforts of research. 
    Section \ref{sec:unify-nes-acceleration}, \ref{sec:spectral-momentum} are our ongoing research which present the answers to the questions. 
    \par
    In Section \ref{sec:unify-nes-acceleration}, we proposed the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures. 
    The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures. 
    The descriptive power of R-WAPG allows convergence analysis for all the variants using one single theorem. 
    \par
    In Section \ref{sec:spectral-momentum} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior. 
    Results of numerical experiments are presented. 
    \par
    Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
    It's based on a series of papers (CITATION HERE) in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
    We will point out potential future direction of research of Catalyst acceleration. 
    \par
    Section \ref{sec:pep}, \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in  nonsmooth optimization frontier research where progress and impacts can be made.

@@

\section{Using PostGreSQL and big data analytic method for species classification on Sentinel-2 Satellite remote sensing imagery}
